Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs

### 2020-05-15 manuscript/manuscript.tex
updates

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W \pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population. We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands. Based on the three band host magnitudes, we find a 1.5~Gyr age and solar metallicity stellar population could well match the color. More detailed information is presented in Appendix~\ref{app:HE0435}.}
%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy. Thus, we infer the color of the lensed arcs in the image plane. Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color. More detailed information is presented in Appendix~\ref{app:HE0435}.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:scaling_relation} 
(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on Equation~\ref{eq:MMlocal}.
(right): offset of $\log(\mathcal M_{\rm BH})$ (vs. \mstar) as a function of redshift. \pink{We plot our new measurements on top of the figure to make direct comparison. The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{Xuheng: Let me know if it's better to remove the blue line and region.}
}
\end{figure*}

@@

\todo{Tommaso please confirm the reference for Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}

>>>>

{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W. \pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population. We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands. Based on the three band host magnitudes, we find a 1.5~Gyr age and solar metallicity stellar population could well match the color. More detailed information is presented in Appendix~\ref{app:HE0435}.}
%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy. Thus, we infer the color of the lensed arcs in the image plane. Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color. More detailed information is presented in Appendix~\ref{app:HE0435}.}

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:scaling_relation} 
(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on Equation~\ref{eq:MMlocal}.
(right): offset of $\log(\mathcal M_{\rm BH})$ (vs. \mstar) as a function of redshift. \pink{We plot our new measurements on top of the figure to make direct comparison. The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{[Xuheng: Let me know if your don't like the current plots.]}
}
\end{figure*}

@@

\todo{Xuheng: Hi Tommaso please confirm if I cite the right reference including Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}
